GMSE: a general tool for management strategy evaluation

### 2017-09-18 notebook/presentation/GMSE_presentation.Rmd
Update with title slides

    par(mfrow = c(5, 1), mar = c(0, 0, 0, 0), oma = c(6, 6, 4, 6));

@@

                          "helping"), bty = "n", cex = 1.5);

@@

@@

@@

@@

@@

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; **Images:** (1) [Public license](https://commons.wikimedia.org/wiki/File:US_and_USSR_nuclear_stockpiles.svg), (2) [Wilkinson 1990](https://projects.ncsu.edu/project/evoresources/Evolutionary%20medicine/Unitsofselection%20DM%20copy/wilkinson-foodsharing.pdf), (3) [Isaacdm](https://commons.wikimedia.org/wiki/File:PhysicsofPenalty.JPG?uselang=en-gb), (4) [Public license](http://www.publicdomainpictures.net/view-image.php?image=180560&picture=brexit-referendum-uk)

@@

@@

@@

@@

```{r, echo = FALSE, fig.height = 6, fig.width = 6}
plot_gmse_effort(agents = sim$agents, paras = sim$paras, ACTION = sim$action, 
                 COST   = sim$cost);
```

@@

## Geese example

[Fox & Madsen 2017 *Ambio* **46(s2)**:170-187](http://doi.org/10.1007/s13280-016-0878-2)
[Fox & Abraham 2017 *Ambio* **46(s2)**:188-197](http://doi.org/10.1007/s13280-016-0879-1)

>>>>

    par(mfrow = c(5, 1), mar = c(0, 0, 0, 0), oma = c(6, 6, 0, 6));

@@

                          "helping"), bty = "n", cex = 1);

@@

# Biodiversity and food security

@@

# Adaptive management and conservation conflicts

@@

- Uses an iterative process of decision-making
- Sets explicit management goals
- Develops alternative management strategies
- Deals with uncertainty by updating knowledge of the system

![](adaptive_management.png)

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Keith et al. (2011) *Biol. Conserv.* **144**: 1175-1778](https://doi.org/10.1016/j.biocon.2010.11.022)

@@

# Game theory in conservation conflict

@@

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; **Images:** (1) [Public license](https://commons.wikimedia.org/wiki/File:US_and_USSR_nuclear_stockpiles.svg), (2) [Wilkinson 1990](https://projects.ncsu.edu/project/evoresources/Evolutionary%20medicine/Unitsofselection%20DM%20copy/wilkinson-foodsharing.pdf), (3) [Isaacdm](https://commons.wikimedia.org/wiki/File:PhysicsofPenalty.JPG?uselang=en-gb), (4) [Public license](http://www.publicdomainpictures.net/view-image.php?image=180560&picture=brexit-referendum-uk)

@@

# Genetic algorithms, and an example using Prisoner's dilemma

@@

# Genetic algorithms in Management Strategy Evaluation

@@

# Rise of the geese: Example use of GMSE

- Wild geese declined starting in the 1930s, likely caused by habitat loss and increased hunting
- Refuges were established and hunting restricted in the 1950s, leading to recovery

![](barnacle_goose.JPG)

**Image:** [Raju Kasambe](https://commons.wikimedia.org/wiki/File:Barnacle_Geese_Branta_leucopsis_London_UK_(4).JPG)

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Fox & Madsen 2017 *Ambio* **46(s2)**:170-187](http://doi.org/10.1007/s13280-016-0878-2)  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Fox & Abraham 2017 *Ambio* **46(s2)**:188-197](http://doi.org/10.1007/s13280-016-0879-1)

![](goose_graph.png)

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Fox & Madsen 2017 *Ambio* **46(s2)**:170-187](http://doi.org/10.1007/s13280-016-0878-2)  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; [Fox & Abraham 2017 *Ambio* **46(s2)**:188-197](http://doi.org/10.1007/s13280-016-0879-1)

@@

```{r, echo = FALSE, fig.height = 6.5, fig.width = 6}
plot_gmse_effort(agents = sim$agents, paras = sim$paras, ACTION = sim$action, 
                 COST   = sim$cost);
```

@@
